\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=black
}
\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\usepackage[margin=1.15in]{geometry}
\linespread{1.25}
\renewcommand*\contentsname{Agenda}
\begin{document}
\begin{center}
CSSS Events Committee Meeting \\
Janurary 10th 2020 \\
\em Meeting called to order by Hun at 10:45am
\end{center}
\tableofcontents
\thispagestyle{empty}
\clearpage
\pagenumbering{arabic} 

\newpage 
\section{Attendes} \label{sec:Introduction}
The following people were in attendance: 
\begin{table}[h]
\centering
\begin{tabular}{cc}
Name                   & SFU Email             \\
Sarbjot Mann           & sarbjotm@sfu.ca       \\
Ryan Lai            & rslai@sfu.ca        \\
Shiva Sanei           & truman\_bui@sfu.ca          \\
Hun Seol & hseol@sfu.ca  
\end{tabular}
\end{table}

\section{Updates} \label{sec:Updates}

\subsection{Hun's Report}
\noindent Hun says that he has talked to Doris and Oliver regarding the White Spot booking for the skating event, and they mentioned that White Spot does not have any discounts available.  There is some talk regarding how many people we can expect show up, and the estimate is from 15-20, so we might want to let White Spot know ahead of time.

\subsection{Cole's Report}
\noindent He's in Calgary and Graduated.

\subsection{Sarbjot's Report}
Room Bookings have been confirmed as mentioned earlier, but Mitch wants to switch to Forum Chambers, because it makes the grant proposal easier and we can have pizza, whereas in TASC we can't have Pizza. Everyone in attendance agrees that Forum Chambers is not the best room to have Board Games in due to its limited space. Cole mentions that we might want to follow up with Kia and Jeffery as they both talked about getting pizza to TASC 9204.


\section{Open Floor} \label{sec: Open}
\subsection{Ice Skating}
\noindent Regarding the Ice Skating event next week, we are still set to do it. Hun will try talk to members in the SLACK on who wants to take what responbility. Some responsibilities are guiding people to the rink, then to White Spot for dinner. \\

\subsection{Mountain Madness}
Regarding the Mountain Madness hackathon, Hun says that he wants to run for it (as there is an election during the next general meeting).  He also thinks that we do not have enough time to plan such a event as it's one month away and 0 planning has taken place so far. He's aiming to have it in Summer instead. \\

\subsection{Promoting Event Committee}
Hun also suggests that he wants to divide the events committee into groups, so one group will be tackling an event at a time. This will allow us to have mor eevents, and have things proceed smoothly. Sarbjot says that while this is a good idea, we'll need more people to attend meetings and in the events committee itself so people are in the same page and so that we can break up into groups. Hun agrees that this is needed, and that he wants to send an application to the mail-list(s) and see who is interested and have them submit an application.  \\

\noindent There is also some concern on how the event committee will function after the April Elections for the CSSS. 

\subsection{Board Games Jan 10}
Shiva asks whose going to run Board Games today, as no one has stepped up. Ryan Lai mentions he's more then happy to as well.
Update: 14:36 thank you to Dusan who also volunteered. 

\section{Delegation of Future Tasks} \label{sec: Future}
\noindent The following tasks have been assigned: \\
- Sarbjot and Hun will talk about promoting the Ice Rink and Sarbjot will send an email \\
- Cole will return to British Columbia \\
- Hun will try and get elected for hackathon chair \\
-  Shiva + Sarbjot + Hun will try and get more people involved in the Events Committee \\
- Ryan will look at doing Board Games today \\

\noindent However, we still need someone to take care of Board Games for the rest of the semester.

\begin{center}
\em{Meeting Adjourned at 11:16am}
\end{center}

\end{document}