\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=black
}
\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\usepackage[margin=1.15in]{geometry}
\linespread{1.25}
\renewcommand*\contentsname{Agenda}
\begin{document}
\begin{center}
CSSS Events Committee Meeting \\
November 25th 2019 \\
\em Meeting called to order by Cole at 10:27am
\end{center}
\tableofcontents
\thispagestyle{empty}
\clearpage
\pagenumbering{arabic} 

\newpage 
\section{Attendes} \label{sec:Introduction}
The following people were in attendance: 
\begin{table}[h]
\centering
\begin{tabular}{cc}
Name                   & SFU Email             \\
Sarbjot Mann           & sarbjotm@sfu.ca       \\
Cole Greer             & cmgreer@sfu.ca        \\
Truman Bui             & truman\_bui@sfu.ca          \\
Nikola Filipovic  & nikolaf@sfu.ca  \\
Doris Chang            & changyic@sfu.ca  \\
Hailey Friesen  & haileyf@sfu.ca
\end{tabular}
\end{table}

\section{Updates} \label{sec:Updates}

\noindent After having some donuts and timbits, the following reports were given 

\subsection{Doris's Report}
\noindent Doris confirms that White-Spot does not do group rates

\subsection{Cole's Report}
\noindent Cole says that he's waiting on information about the Grant, and seeing how SFSS approves it. He also mentions that because of the proposed transit strike on Wednesday, Thursday and Friday there is a concern about the number of people who will attend. He suggests that we could do a BBQ on the last day of classes (Monday) but is unsure about what paperwork has to be filed and if SFSS wants advanced notice / how many days in advance does the paperwork have to be done by. 

\subsection{Sarbjot's Report}
Room Bookings have been confirmed by Jay. Sarbjot also mentions that he has booked the last friday and last day of classes for last semester as he was unsure which day we wanted to do EoSS for next semester, as it's easier to remove bookings then to book days. 


\subsection{Discussions on Reports}
\noindent Cole asks Sarbjot what the progress of Secret Santa was, Sarbjot says that VJ told him that he's (VJ) is not planning on doing it because of a short notice and because of the bus strike. \\

\noindent Cole then asks the people in attendance what they think of doing a BBQ on Monday, his opinion is that he prefers Ilia because the grant is set up for Ilia specifically, and since the BBQ will be last minute things won't be as organized as he likes. After some discussion, it is decided that we'll stick with Ilia because we don't know what the schedule for transit is for Monday, as busses seem to be getting cancelled after 16:00, because of this the BBQ will have to be held before then, but there is conflict with classes. Cole will also talk to Ilia about how the expected attendance will decrease.  \\ 

\section{Open Floor} \label{sec: Open}
\noindent Sarbjot asks if we would like to discuss roles for next semester as talked about at the previous meeting. Cole says that would depend on who joins the event committee next semester as currently the only roles that are needed are someone to take minutes, someone to chair and possibly design posters.  There is also mention that Celina or Nikola will most likely chair meetings as Cole will be graduating this term.  
\begin{center}
\em Congratulations Cole!  
\end{center}

\section{Delegation of Future Tasks} \label{sec: Future}
\noindent The following tasks have been assigned: \\
- Sarbjot will book TASC 9204 for Monday, December 2nd as a backup plan\\
- Cole will talk to Ilia and inform them about the possibly that less people may show up  \\
\begin{center}
\em{Meeting Adjourned at 10:45am}
\end{center}

\end{document}